%---------change this every homework
\def\yourid{mst3k}  % substitute your userED
\def\collabs{collaborators} % substitute your collaborators
\def\sources{sources} % substitute your sources
% -----------------------------------------------------
\def\duedate{October 29, 2025 at 11:59p}
\def\pnumber{6}
%-------------------------------------

\documentclass[10pt]{article}
%\documentclass[tikz,border=10pt]{standalone}
\usepackage{dsa2}
\usepackage{float}
\usepackage{tikz}
\usepackage{listings}

\usepackage{xcolor}

\begin{document}
\thispagestyle{empty}
\handout


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{problem} Numerical Coverage \end{problem}

You are given a set of points $P= \{ p_1, p_2, \ldots, p_n \}$ on the real line (you may assume these are given to you in sorted order). 

\begin{enumerate}

  \item Describe an algorithm that determines the smallest set of unit-length closed intervals that contains all of the given points. For example, the points $\{0.9,1.2,1.3,2.1,3.0\}$ can be covered by $[0.7,1.7]$ and $[2.0,3.0]$. State the runtime of your algorithm.



  \solution{
    % Your solution here
  }
  


  \item Prove that the problem has {\em optimal substructure}.

  \solution{
    % Your solution here
  }
  


  \item Prove that your algorithm's greedy choice returns the optimal result.

  \solution{
    % Your solution here
  }

\end{enumerate}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{problem} Skiing \end{problem}

Consider a situation in which you have $n$ skiers with heights $p_1, p_2, \ldots, p_n$, and $n$ pairs of skis with length $s_1, s_2, \ldots, s_n$. The problem is to assign each person a pair of skis so that the overall difference between the height of a skier and the length of their skis is minimized. More precisely, if $\alpha(i)$ returns the index of the skis assigned to person $p_i$, we want to minimize:

\[ \frac{1}{n} \sum_{i=1}^{n} \left( \left| p_i - s_{\alpha(i)} \right| \right) \]

\noindent Consider two greedy algorithms that may solve this problem:

\begin{enumerate}
  \item Find the skier and skis whose height difference is minimized. Assign those skis to that skier and repeat.
  \item Pair the smallest skier with the smallest skis, second smallest skier to second shortest skis, etc. until all pairings are complete.
\end{enumerate}

\noindent One of these greedy algorithms is correct. You must do three things: 

\begin{enumerate}



  \item Prove this problem has optimal substructure. 

  \solution{
    % Your solution here
  }



  \item Claim which of the two algorithms is correct. 

  \solution{
    % Your solution here
  }



  \item Show the greedy choice property of your chosen algorithm by using an exchange argument.

  \solution{
    % Your solution here
  }

\end{enumerate}

\end{document}
